---
title: "Regression Analysis"
output: html_notebook
---

In this project, we will be using **Regression backward selection** for our analysis. The label for our data will be the rating.

```{r}
## first the imports
library(tidyverse)
library(broom)
library(GGally)
```

We need to first check to see if there's actually a linear relationship between the feature and labels.

```{r}
performance <- read_csv('../data/performance.csv')
glimpse(performance)
## using ggpairs to check the relationships
ggpairs(performance)
```

And we do actually see some linearity in the plots with overall_rating.

We will use the t-statistic to decide which variables are not as useful for our model and can be discarded. We will keep on this process until we have a t-statistic of \< 1.

```{r}
## for our linear model
## we have to first pass in the variable
## that we'd like our model to explain
## and then use . trick to have it use
## the rest of the columns as the input features
model <- lm(overall_rating ~ .,
            data = performance)
## and we can look at the summary of our model
summary(model)
```

Given the above summary, at the first glance we can say that given the high t-values and low probability for "handles_employee_complaints" and "space_for_learning", these two features are the most useful ones in our model. Considering the current values, the first feature that we will remove is the "not_overly_critical".

```{r}
## for our new model
## we can simply update the previous one
## the following way
## by using - not_overly_critical 
## from the right side
model_1 <- update(model,
                  . ~ . - not_overly_critical)
summary(model_1)
```

Given the updated model, now the next feature that could be removed is the "raises_for_performance", where we have the lowest t-value.

```{r}
## so we will be uodating our model once again
model_2 <- update(model_1,
                  . ~ . - raises_for_performance)
summary(model_2)
```

The next feature that can be removed is the "no_special_privileges", which has the highest absolute t-value in our remaining features.

```{r}
model_3 <- update(model_2,
                  . ~ . - no_special_privileges)
summary(model_3)
```

Now, all of absolute t-values are above 1, and we can stop removing features at this point.
